---
title: "Lab 1: Exploratory Data Analysis"
subtitle: "This Bitter Earth"
author: "YILIN LI"
output: pdf_document
---

* * *

#### Exercise 1

```{r}
library(MASS)
dim(Boston)
```

The Boston Dataframe has 506 rows and 14 columns. Each row represents 1 observation, which is Boston housing value and each column represents 1 feature recorded. 

#### Exercise 2

```{r}
pairs(Boston[,c(1,10)])
pairs(Boston[,c(3,5)])
```

- crime rate is correlated to the level of tax 
- the higher industry density, the higher nitrogen oxides concentration

#### Exercise 3

```{r}
plot(Boston$age, Boston$crim)
plot(Boston$dis, Boston$crim)
plot(Boston$lstat, Boston$crim)
plot(Boston$medv, Boston$crim)
```

- more built prior to 1940, the higher the criminal rate. 
- closer to the employment centres, the higher the criminal rate.
- more populations are in lower status, the higher the criminal rate. 
- the less the owner-occupied homes in $1000, the higher the criminal rate. 

#### Exercise 4

```{r}
length(Boston$crim[Boston$crim>20])
hist(Boston$crim[Boston$crim>1],breaks = 25)
```

Most suburbs have the criminal rate lower than 20%, but there are 18 suburbs have the criminal rate higher than 20% even reaching 80%. 

```{r}
hist(Boston$tax,breaks = 25)
```

There's a large divide between suburbs taxing from 200 to 400 and a huge peak taxing at 660-680.

```{r}
hist(Boston$ptratio,breaks = 25)
```

The pupil-teacher ratio skew towards higher ratio and has a peak at 20-21. 

#### Exercise 5

```{r}
dim(subset(Boston, chas==1))[1]
```

35 suburbs bound the Charles River.

#### Exercise 6

```{r}
median(Boston$ptratio)
```

The median pupil-teacher ratio is 19.05. 

#### Exercise 7

The input is a $506 \times 14$ matrix $X \in R^{506\times14}$, where each row is a suburb data. The response is a column vector $y \in R^{506}$ represents the predicted average value of the home for each suburb data. 
